A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-07-18 paper.tex
outlined sections
starting to work on methods
updating paper and meth
intro added
Update on Overleaf.
23, May from SF
Shinichiro_30May
acks, key words, nies address
add software availability

%%% ELS includes
\documentclass[review]{elsarticle}
\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\journal{Environmental Modelling \& Software}
\bibliographystyle{elsarticle-num}
%%%

@@

%%% ELS input
\input{elsfrontmatter} 
%%%

\newpage
stuff
%% \input{intro}
%% \input{methods}
%% \input{results}
%% \input{conclusion}
%

@@

fill in

>>>>

%%% ELS includes
% * <sfujimori112256@gmail.com> 2017-05-23T14:15:19.404Z:
% 
% comment from SF
% 
% ^ <sfujimori112256@gmail.com> 2017-05-24T18:49:42.852Z.
\documentclass[review]{elsarticle}
\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\journal{Environmental Modelling \& Software}
\bibliographystyle{elsarticle-num}
%%%

@@

%%% ELS input
\input{elsfrontmatter} 
%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Software Availability}

\texttt{aneris}, first made available in 2017, is available online at
\url{https://github.com/gidden/aneris} as a free and open-source Python software
library (approximately 2000 lines of code). The \texttt{aneris} software was
developed by the lead author, Matthew J. Gidden, Ph.D., whose contact
information is shown on the title page of this manuscript. Documentation for the
\texttt{aneris} Python package, including software requirements, is available
\href{http://mattgidden.com/aneris/}{online}.

\newpage

\include{intro}
\include{meth}
\include{results}
% * <sfujimori112256@gmail.com> 2017-05-25T05:18:35.016Z:
% 
% I think the current results are basically fine (sorry I have not read in detailed though).  What we should show and discuss are pretty much depending on how we evaluate these results. So, at this stage, I would like to put more comments on this section
% 
% 
% ^.
\include{future}

@@

The authors would like to acknowledge a number of colleagues who helped
contribute both discussion and feedback for this work, including Drs. Detlef van
Vuuren, Elmar Kriegler, Gunnar Luderer, and Joeri Rogelj. The authors further
with to thank \TODO{who?} for their generous funding of this effort.
